Finite Property Convex Elicitation Notes

### 2018-09-28 jessie-writeup/jessie-writeup.tex
Updates to Jessies writeup

\begin{definition}
Let $\Gamma$ be a labeled property.
Define $\text{strip}(\Gamma) := \{ \Gamma_r : r \in \R \}$.
Informally, strip removes labels from the property.
\end{definition}

@@

\begin{definition}
A property $\Gamma$ is \emph{finite} if $\im(\Gamma) := \{r\in\Gamma(p) : p\in\Delta(\Y)\} = \bigcup_{p\in\Delta(\Y)} \Gamma(p)$ is a finite set.
%\jessie{Take 2:}  A property $\Gamma$ is \emph{finite} if there are only finitely many full-dimensional level sets.
\end{definition}

\begin{lemma}\label{conj:closed-level-sets}
  Let $\Gamma$ be elicitable.
  For any $r\in\R$, the level set $\Gamma_r = \{ p \in \Delta(\Y) : \Gamma(p) = r \}$ is closed.
\end{lemma}
\begin{proof}[Proof sketch]
  Let $L$ elicit $\Gamma$.
  The function $G(p) = -\min_{r\in\R} \E_p L(r,Y) = -\E_p L(\Gamma(p),Y)$ (taking any $r\in\Gamma(p)$ in case of ties) is convex.
  There exists $\D \subseteq \partial G$ and some bijection $\varphi : \R \to \D$ with $\Gamma(p) = \varphi^{-1}(\D\cap \partial G_p)$.
  Thus, $\Gamma_r = \{p : r\in\Gamma(p)\} = \{p : \varphi(r) \in \D\cap\partial G_p\} = \{p : \varphi(r) \in \partial G_p\}$, which is closed by convex analysis -- use \url{https://arxiv.org/pdf/1211.3043.pdf}.
	See [Raf/Ian, above (Cor 3.11) with their Thm 3.5 and Rockefellar 24.4]  
\end{proof}

Notes before starting:
\begin{itemize}
\item (Assuming the metric space is $(\Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?).
We just use this looking at interiors of level sets.
\item The interior of a level set $X$ is defined as $\inter{X} = \{p \in X: \epsilon > 0,  \forall q \in B(\epsilon,p), \argmin_rE_p L(r,Y) = \argmin_r E_q L(r,Y)\}$
\item A level set is \emph{full-dimensional} if dim(affine hull($\Gamma_r$)) is equal to dim($\Delta(\Y)$). 
\item A full-dimensional level set has non-empty interior.
\end{itemize}

\section{Conjecture turned Lemma}

\begin{lemma}\label{lem:intersect-lev-sets}
  Let the elicitable property $\Gamma$ have a finite set $\Theta$ of full-dimensional level sets, so that for all $\theta \in \Theta$,  there is a unique optimal report $r_\theta$ for all $p \in \inter{\theta}$.
  Consider the finite set $\R' := \{ r_\theta\}_{\theta \in \Theta}$.
  Then for every $r \in \R$, there exists a finite set $R \subseteq \R'$ so that $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$.
\end{lemma}
\jessie{To show: can find set $R$ s.t. $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$, and $R$ is finite.}
\begin{proof}
  \emph{Facts used: Level sets are closed, non-degeneracy of level sets}\\

\hrule
\bigskip
  Note:    As $\Gamma$ is non-degenerate, we know for all $p \in \P$ that $|\Gamma(p)| \geq 1$.
  For any $p \in \P$, if $|\Gamma(p)| = 1$, then $\Gamma(p) = r \in \R'$, so we can choose $S := \{r\} \subseteq \R'$ so that $\Gamma_r = \cap_{r \in S} \Gamma_r$.

@@

As level sets are closed (by Lemma \ref{conj:closed-level-sets}), $\Gamma_{r_i} = cl(\Gamma_{r_i})$, so $q \in \Gamma_{r_i}$.
%Thus as $q \in \Gamma_r \implies q \in \Gamma_{r_i}$ for all $r_i \in S_r$, $q \in \Gamma_r \implies q \in \cap_{r_i \in S} \Gamma_{r_i}$.
Thus as $q \in \Gamma_r \implies q \in \Gamma_{r_i}$ for all $r_i \in S_r$, we observe $\Gamma_r \subseteq \cap_{r_i \in S}\Gamma_{r_i}$.

@@

\section{Formal Statements and modifications needed to prove}

@@

\subsection{Main statement}

@@

As $\Gamma \leq \Gamma$, then by Lemma \ref{lem:define-trim}, $\trim(\Gamma) = \strip(\Gamma)$.

@@

$1 \implies 2$. 
% \emph{Assumptions used: non-redundancy}

Consider $\strip(\Gamma) = \{\Gamma_r : r \in \R \}$.
Let us construct the finite set $\R' = \{r_\theta \}_{\theta \in \Theta}$.
Clearly, $\R' \subseteq \R$.

We can rewrite $\strip(\Gamma) = \{\Gamma_{r'} : r' \in \R' \} \cup \{\Gamma_{r} : r \in \R \setminus \R' \}$.
As the first set is finite, we just need to show $\{\Gamma_{r} : r \in \R \setminus \R' \}$ is finite in order to show $\strip(\Gamma)$ is finite.

Let us consider some $r\in\R \setminus \R'$.
The level set $\Gamma_r = \{p : \Gamma(p) = r\}$ by definition.
As $r \not\in \R'$, the interior is empty; that is, $\inter{\Gamma_r} = \emptyset$.
% For any $p \in \Gamma_r$, then, there is some $q \in B(\epsilon, p)$ such that $\E_q L(r', Y) < \E_q L(r,y)$ for some $r' \in \R'$.
% As $r = \argmin_{\tilde{r}} \E_p L(\tilde{r}, Y)$, then we observe $\E_p L(r, Y) = \E_p L(r', Y) = \min_{\tilde{r}}\E_p L(\tilde{r}, Y)$ for $p \in \Gamma_r$. 
% Thus, $\Gamma_r \subseteq \Gamma_{r'}$.
By Conjecture \ref{lem:intersect-lev-sets}, there exist a set of finite reports $R \subseteq \R'$ such that $\bigcap_{r'\in R} \Gamma_{r'} = \Gamma_r$.
As the set $\R'$ is finite, then the power set $2^{\R'}$ is finite.
Thus, the set $\{ \Gamma_r : r \in \R \setminus \R' \} =  \{ \bigcap_{r_1 \in R} \Gamma_{r_1} : R \subseteq \R' \}$ is finite.

The union of a two finite sets is then finite, so $\trim(\Gamma) = \strip(\Gamma) = \{ \Gamma_{r'} : r' \in \R' \} \cup \{ \Gamma_r : r \in \R \setminus \R' \}$ is finite.

% Since $\Gamma$ is finite, we know it only has finitely many FDLS, and since $\Gamma$ is convex, these level sets are convex.
% On the interior of these level sets, we know there is a unique optimal report.
% As $\R' = \bigcup_{\Gamma_r \text{is FDLS}}r$, $\R'$ is finite as the finite union of finite sets is finite.
% By Lemma 2 from original writeup, or new definition of trim, we know that $L|_\R$ elicits trim($\Gamma$).
% As the new report set is finite, there many only be a finite number of minimizing reports.

% Consider the full-dimensional level sets of $\Gamma$: as $\R' \subseteq \R$, then when $L$ is restricted to $\R'$, for any $r \in \R$, there must be some $r' \in \R'$ such that $\Gamma_{r} \subseteq \Gamma_{r'}$, as if .

%Since $\Gamma$ is a finite property, there are a finite number of (non-empty) level sets.
%As there is only one optimal report per (interior of) level set, there are a finite of minimizing reports.
%Let this finite set be $\tilde{\R}$, and observe $\tilde{R}$ is finite.
%By definition, $\tilde{\R} \subseteq \R$.
%As $\im(\Gamma') = \im(\Gamma) \cap \R = \tilde{\R} \cap \R'$ \footnote{Needs showing}, then the finite intersection of a finite set and another set is finite, so $\im(\Gamma')$ is finite.

\bigskip
$2 \implies 1$.  
\emph{Assumptions used: Nondegeneracy, elicitability of $\Gamma$}

Let $\Theta := \trim(\Gamma)$ be a finite set.
By construction, $\Theta$ is a set of level sets defining the property $\Gamma$.
As $\Theta$ is finite, $\Gamma$ then only has finitely many level sets, and therefore, finitely many \emph{full-dimensional} level sets.
We construct the set $\R' := \{r \in \R : \{r\} = \argmin_r \E_p L(r,Y) \text{ for } p \in \inter{\theta}; \theta \in \Theta \}$.
Consider a full-dimensional level set $\theta = \Gamma_r \in \Theta$ for some $r \in \R'$.
As $\Theta$ is finite, we just want to show that there is a unique optimal report on the interior of each $\theta \in \Theta$.
As $\trim(\Gamma) = \strip(\Gamma')$ for the constructed $\Gamma'$, we just need to show $\Gamma'$ is nondegenerate, as uniqueness of the optimal report on each interior follows from the construction of $\R'$.

Suppose there was a distribution $p \in \inter{\theta}$ for some $\theta \in \Theta$ such that $\Gamma'(p) = \emptyset$.
Then $\Gamma(p)$ is set-valued, since $\Gamma$ is nondegenerate, and every $r \in \Gamma(p) \not\in \R'$.
Suppose there were some $r_1, r_2 \in \R$ (this generalizes) so that $r_1, r_2 \not \in \R'$ but $\{r_1, r_2\} = \Gamma(p)$ for some $p \in \inter{\theta}$.
Then (WLOG) $\Gamma_{r_1} = \theta$ and we know $\Gamma_{r_2} \subseteq \Gamma_{r_1} = \theta$.
As $r_1 \not\in \R$, for every $p \in \inter{\theta}$ we know $r_1$ must not be the unique minimizer.
If $\Gamma_{r_2} \subseteq \Gamma_{r_1}$, then the property $\tilde \Gamma := \Gamma \cap (\R' \cup \{r_1\})$ is nonempty at the distribution $p$ in question and $\strip(\Gamma') = \strip(\tilde \Gamma)$.

If these possible empty values of $\Gamma'$ at multiple distributions, the same argument need only be applied finitely many times, so there is a nondegenerate $\tilde \Gamma$ such that $\strip(\tilde \Gamma) = \trim(\Gamma)$ has a unique optimal report on the interior of each level set.

Thus, 2$\implies$ 1.

\jessie{Ran out of time, but not satisfied with this completely.}

%For contradiction, suppose there was some $s \in \R$ such that $\E_p L(s,Y) = \E_p L(r_\theta, Y)$ for some $p \in \inter{\theta}$.
%
%As $p \in \inter{\theta}$, we then know $\E_q L(r_\theta, Y) \leq \E_q L(s,Y)$ for all $q \in B(\epsilon, p)$.
%Therefore, $\Gamma_s \subseteq \inter{\Gamma_{r_\theta}} \subseteq \Gamma_{r_\theta}$.
%As there are no dominated reports (by non-redundancy of $\Gamma$), this implies $\Gamma_s = \Gamma_{r_\theta}$.
%Therefore, we can see that $r_\theta = s$, since otherwise we would contradict non-redundancy of $\Gamma$.
%As $r_\theta = s$, we can then say $r_\theta$ is the unique property value on $\inter{\theta}$.
%Therefore, $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
%
%As the full-dimensional level sets in $\Theta$ are finite and the optimal report is unique on the interior of level sets, $2 \implies 1$.

@@

>>>>

\begin{definition}
Let $\Gamma$ be a labeled property.
Define $\text{strip}(\Gamma) := \{ \Gamma_r : r \in \R \}$.
Informally, strip removes labels from the property.
\jessie{Strip includes the boundaries of level sets / lower dimensional level sets.}
\end{definition}

@@

\begin{definition}
A property $\Gamma$ is \emph{finite} if $\im(\Gamma) := \{r\in\Gamma(p) : p\in\Delta(\Y)\} = \bigcup_{p\in\Delta(\Y)} \Gamma(p)$ is a finite set.
\end{definition}

\begin{definition}\label{def:unlabeled-nonredundant}
  An unlabeled property $\Theta$ is \emph{nonredundant} if for any full dimensional $\theta_1, \theta_2 \in \Theta$ we observe $\theta_1 \cap \theta_2 = \emptyset$ almost everywhere.
\end{definition}

Other notes before starting:
\begin{itemize}
\item (Assuming the metric space is $(\Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?).
We just use this looking at interiors of level sets.
\item The measure $\mu$ is arbitrary, but why not use Lebesgue measure on $\Delta(\Y) \subset \reals^{|\Delta(\Y)|-1}$
\item The interior of a level set $X$ is defined as $\inter{X} = \{p \in X: \epsilon > 0,  \forall q \in B(\epsilon,p), \argmin_rE_p L(r,Y) = \argmin_r E_q L(r,Y)\}$
\item Define the boundary $bd(X) := cl(X) \setminus \inter{X}$.
\item A level set is \emph{full-dimensional} if dim(affine hull($\Gamma_r$)) is equal to dim($\Delta(\Y)$). 
\item A full-dimensional level set has non-empty interior.
\end{itemize}

\section{Conjectures (to prove)}

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma$ be a nondegenerate elicitable property \jessie{with a finite set of level sets.}
	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \leq \Gamma$ and $\trim(\Gamma) = \strip(\Gamma')$.  
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets.}

	To start, construct $\R' \subseteq \R := \{ r \in \R : \inter{\Gamma_r} \neq \emptyset \}$.
	Clearly, $\R'$ is finite.
	Define the property $\Gamma' = \Gamma\cap \R'$.
	We want to show that the constructed $\Gamma'$ is nondegenerate and nonredundant.
	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$.
	If $p \in \inter{\Gamma}_r$, then by construction of $\R'$, we see $r \in \R'$.

	Thus, we just need concern ourselves with $p \not \in \inter{\Gamma_r}$.
	As $\Gamma$ is nondegenerate, there are then $n$ level sets $\{\Gamma_{r_i}\}_{i=1}^n, \in \R$ in the $\epsilon$-ball around $p$.
	We claim some $r_i$ is in $\R'$.
	Since there are only a finite set of level sets, at least one in the $\epsilon$-ball centered on $p$ is full dimensional.
	Therefore, there is some $r_i \in \R'$ so that $p \in cl(\Gamma_{r_i})$, and as level sets are closed by Lemma~\ref{lem:closed-level-sets}, we then observe $p \in \Gamma_{r_i}$.
	Therefore $\Gamma'$ is nondegenerate.

	Now to show $\Gamma'$ is nonredundant.
	For contradiction, suppose $\Gamma'$ is redundant.
	Then there are $r_1, r_2 \in \R'$ with $r_1 \neq r_2$ so that either $\Gamma'_{r_1} \subsetneq \Gamma'_{r_2}$ or $\Gamma'_{r_1} = \Gamma'_{r_2}$.

	First, suppose $\Gamma'_{r_1} = \Gamma'_{r_2}$
	Since we can think as the property values as labelings of the subgradient sets (denoted by $\partial$) of the the concave Bayes Risk $G(p)$.
	\jessie{Need source?}
	As $G$ is concave, it is differentiable almost everywhere, which means that for everywhere but a $\mu$-null set, $|\partial G(p)| = 1$.
	Then $\Gamma'(p) = \partial G(p) \implies |\Gamma'(p)| = 1$ almost everywhere, which-- along with the fact that the level sets $\Gamma'_{r_1}$ and $\Gamma'_{r_2}$ are full dimensional (and therefore have positive measure since they are convex), contradicts the claim $r_1 \neq r_2$.
	Thus we conclude there aren't reports $r_1, r_2 \in \R'$ so that $r_1 \neq r_2$ and $\Gamma'_{r_1} = \Gamma'_{r_2}$.

%	By construction of $\R'$, we know both $\Gamma'_{r_1}$ and  $\Gamma'_{r_2}$ are full dimensional.
%	If $\Gamma'_{r_1} = \Gamma'_{r_2} = \Gamma'_{r_1} \cap \Gamma'_{r_2}$ are full dimensional, this contradicts something?

	Otherwise suppose $\Gamma'_{r_1} \subsetneq \Gamma'_{r_2}$.
	As $\Gamma'_{r_1}$ is full-dimensional, so is $\Gamma'_{r_1} \cap \Gamma'_{r_2} = \Gamma'_{r_1}$.
	Again, since we know that $|\Gamma'(p)| = 1$ almost everywhere, and as the intersection of the two level sets is full-dimensional, this again contradicts the differentiability of $G$ almost everywhere, since the intersection of the level sets has positive measure in the simplex.
	Therefore, $\Gamma'$ is nonredundant.

	Finally, by definition of $\trim(\Gamma)$, we conclude $\Gamma'$ is a nondegenerate, nonredundant property such that $\trim(\Gamma) = \strip(\Gamma')$.

\begin{conjecture}\label{conj:trim-full-dim}
	Every level set of $\Theta := \trim(\Gamma)$ is full-dimensional  
\end{conjecture}

\begin{proof}[Proof Sketch]
	\emph{Uses: Conjecture~\ref{conj:gam-prime-exists}.  Claim: $\strip(\Gamma')$ is nonredundant.}

	In order to understand $\trim(\Gamma)$ is, we use the $\Gamma' \leq \Gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and let $\R'$ be the set such that $\Gamma' = \Gamma\cap \R'$.
	First, we see $\Theta = \strip(\Gamma')$ is nonredundant in the unlabeled sense as $\Gamma'$ is nonredundant in the labeled set from Conjecture~\ref{conj:nonredundant-defs-equivalent}, since we know $\Gamma'$ is nonredundant-- and well-defined from Conjecture~\ref{conj:gam-prime-exists}.
	\jessie{To show.}

	For contradiction:
	Let $\theta \in \Theta$ not full-dim and non-redundant (whatever that means for an unlabeled property-- see definition \ref{def:unlabeled-nonredundant} section for proposed definition).

	We now show that every level set $\theta \in \Theta = \strip(\Gamma') = \trim(\Gamma)$ is full dimensional.

	We proceed in 2 cases for a level set $\theta \in \Theta$:
	\begin{enumerate}
		\item For all $\theta' \in \Theta$, $\theta \cap \theta' = \emptyset$.
		We know the level set $\theta$ is closed by Lemma~\ref{lem:closed-level-sets}
		By definition of $\R'$, there is some $p \in \inter{\theta}$ so that for $r_\theta = \Gamma'(p)$, there is a ball $B(\epsilon, p)$ centered around $p$ so that for every $q \in B(\epsilon, p)$, $r_\theta \in \Gamma'(q)$.
%		(In fact, as $\Theta$ is nonredundant, we claim $r_\theta = \Gamma'(q)$. \jessie{Need to show?})
		Therefore, the level set $\Gamma_{r_\theta} = \theta$ is full dimensional as it has nonempty interior.

		Intuitively, this can be seen since the interior of $\theta$ is nonempty by nondegeneracy of $\Gamma'$.

		\bigskip
		\hrule
		Other notes from meeting:\\
		Use closure and nondegeneracy

		Look at subset topology? ($\tau_{\R'} := \{\R' \cap U : U \in \tau \}$.)

		\hrule
		\item Exists $\theta' \in \Theta$, $\theta \cap \theta' \neq \emptyset$.

		By nonredundancy of $\Gamma'$, we then observe nonredundancy of $\Theta$, we know that $\mu(\theta \cap \theta') = 0$.
		We want to show that $\theta$ is full dimensional.
		\jessie{TODO}

		\bigskip
		\hrule
		Other notes from meeting:\\
		Look at expected loss/score of $\Gamma'$.
		\hrule
	\end{enumerate}

	Therefore, we have a contradiction and conclude $\theta \in \trim(\Gamma)$ is full dimensional. 
\end{proof}

\begin{conjecture}\label{conj:nonredundant-defs-equivalent}
	An elicitable property with finite level sets $\Gamma$ is nonredundant (in the labeled definition) $\iff$ $\strip(\Gamma)$ is nonredundant (in the unlabeled definition.)
\end{conjecture}
\begin{proof}
	We show both directions.\\
	\begin{enumerate}
		\item [$\implies$]
		Let the property $\Gamma:\P \to \R$ be nonredundant.
		Then for any two reports $r, r' \in \R$ with $r \neq r'$, the level sets $\theta := \Gamma_r \not \subseteq \Gamma_{r'}$ and $\theta' := \Gamma_{r'} \not \subseteq \Gamma_r$.
		In what follows, $G : \P \to \R$ is the Bayes Risk, or optimal report given a distribution $p$.
		Each report $r$ corresponds to a labeling of the subgradient sets of $G$.

		\jessie{Doesn't really use the assumption at all... uses concavity of Bayes Risk.}

		For notation, we write the set $S := \{p \in \P : |\partial(G(p))| > 1\}$

		Then consider the set $\theta \cap \theta'$.

%		Suppose for contradiction that $\inter{(\theta \cap \theta')} \neq \emptyset$.
%		Then there is some $s \in \inter{(\theta \cap \theta')}$ so that $p \in B(\epsilon, s) \implies p \in \inter{(\theta \cap \theta')}$.
%		As the ball $B(\epsilon s)$ is convex with nonempty interior, it has positive measure, and by monotonicity of a measure, we say $0 < \mu(B(\epsilon, s)) \leq \mu(\inter{(\theta \cap \theta')})$.

		Since the property $\Gamma$ is elicitable, the Bayes Risk is strictly convex-- meaning it is differentiable almost everywhere, thus $\mu(S) = 0$.

		Since we assume $r \neq r'$, we observe that $(\theta\cap\theta') \subseteq S$.
		By monotonicity of $\Gamma$, since $(\theta\cap\theta') \subseteq S$, we know $\mu(\theta \cap \theta') \leq \mu(S) = 0$.

%		This, however, contradicts the positive measure of the interior.
%		Therefore, it must be the case that the interior has Lebesgue measure $0$.

		Since $0 \leq \mu(\theta \cap \theta') \leq \mu(S) = 0$, we observe the unlabeled definition of nonredundancy.

		\item[$\impliedby$] 
		Say that for any two full dimensional level sets $\theta, \theta' \in \Theta := \strip(\Gamma)$ that $\mu(\theta \cap \theta') = 0$.
		Then there are reports $r, r' \in \R$ such that $\theta = \Gamma_r$ and $\theta' = \Gamma_{r'}$.
		As $\mu(\Gamma_r \cap \Gamma_{r'}) = 0 \implies$ the interior of $\Gamma_r \cap \Gamma_{r'}$ is empty.
		Therefore, the intersection of the two level sets is not full dimensional.

		As $\theta, \theta'$ are both full dimensional, than their intersection not being full dimensional implies they only share optimal reports on the boundary. \jessie{To cite?}

		Therefore, we can see that $\theta \not \subseteq \theta'$ as $\theta \neq \theta' \cap \theta$, nor are they equal as their intersection is lower dimensional.

		Therefore, $\strip(\Gamma)$ is nonredundant $\implies \Gamma$ is nonredundant.
	\end{enumerate}

\section{Lemmas}

\begin{lemma}\label{lem:closed-level-sets}
	Let $\Gamma$ be elicitable.
	For any $r\in\R$, the level set $\Gamma_r = \{ p \in \Delta(\Y) : \Gamma(p) = r \}$ is closed.
\end{lemma}
\begin{proof}[Proof sketch]
	Let $L$ elicit $\Gamma$.
	The function $G(p) = -\min_{r\in\R} \E_p L(r,Y) = -\E_p L(\Gamma(p),Y)$ (taking any $r\in\Gamma(p)$ in case of ties) is convex.
	There exists $\D \subseteq \partial G$ and some bijection $\varphi : \R \to \D$ with $\Gamma(p) = \varphi^{-1}(\D\cap \partial G_p)$.
	Thus, $\Gamma_r = \{p : r\in\Gamma(p)\} = \{p : \varphi(r) \in \D\cap\partial G_p\} = \{p : \varphi(r) \in \partial G_p\}$, which is closed by convex analysis -- use \url{https://arxiv.org/pdf/1211.3043.pdf}.
	See [Raf/Ian, above (Cor 3.11) with their Thm 3.5 and Rockefellar 24.4]  
\end{proof}

\begin{lemma}\label{lem:intersect-lev-sets}
  Let the elicitable property $\Gamma$ have a finite set $\Theta$ of full-dimensional level sets, so that for all $\theta \in \Theta$,  there is a unique optimal report $r_\theta$ for all $p \in \inter{\theta}$.
  Consider the finite set $\R' := \{ r_\theta\}_{\theta \in \Theta}$.
  Then for every $r \in \R$, there exists a finite set $R \subseteq \R'$ so that $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$.
\end{lemma}
%\jessie{To show: can find set $R$ s.t. $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$, and $R$ is finite.}
\begin{proof}
  \emph{Facts used: Level sets are closed (Lemma \ref{lem:closed-level-sets}), non-degeneracy of $\Gamma$.}\\

  Note:    As $\Gamma$ is non-degenerate, we know for all $p \in \P$ that $|\Gamma(p)| \geq 1$.
  For any $p \in \P$, if $|\Gamma(p)| = 1$, then $\Gamma(p) = r \in \R'$, so we can choose $S := \{r\} \subseteq \R'$ so that $\Gamma_r = \cap_{r \in S} \Gamma_r$.

@@

As level sets are closed (by Lemma \ref{lem:closed-level-sets}), $\Gamma_{r_i} = cl(\Gamma_{r_i})$, so $q \in \Gamma_{r_i}$.
%Thus as $q \in \Gamma_r \implies q \in \Gamma_{r_i}$ for all $r_i \in S_r$, $q \in \Gamma_r \implies q \in \cap_{r_i \in S} \Gamma_{r_i}$.
Thus as $q \in \Gamma_r \implies q \in \Gamma_{r_i}$ for all $r_i \in S_r$, we observe $\Gamma_r \subseteq \cap_{r_i \in S}\Gamma_{r_i}$.

@@

@@

\section{Main statement}

@@

@@

\begin{enumerate}
\item [$1 \implies 2$]
Consider the finite set $\R' := \{r_\theta\}_{\theta \in \Theta}$.
Clearly, $\R' \subseteq \R$.
We construct the property $\Gamma' := \Gamma \cap \R'$ so that $\Gamma' \leq \Gamma$.
If we can show $\Gamma'$ is nondegenerate and nonredundant, we can then show $\strip(\Gamma')$ is finite, which is $\trim(\Gamma)$ by definition.

Since there is an optimal report $r_\theta \in \Gamma'(p)$ for every $p \in \inter{\theta}$ and level sets are closed, there is then an optimal report $r_\theta \in \Gamma'(p)$ for every $p \in \theta$.
Therefore, $\Gamma'$ is nondegenerate.

To see $\Gamma'$ is nonredundant, consider the assumption of uniqueness of the optimal report on the interior of each level set.
Thus, a report could only be redundant on the boundary of a level set.
As $\R'$ is constructed to only contained optimal reports for full dimensional level sets, any $r$ such that $\Gamma_r$ is not full dimensional is not an element of $\R'$.
For any $r, r' \in \R'$ with $r \neq r'$, we can see that $\Gamma_r \neq \Gamma_{r'}$ as both level sets are full dimensional and  on the (nonempty) interior of each level set, the respective report us uniquely optimal by assumption.
To see (WLOG) $\Gamma_{r'} \not \subset \Gamma_r$, consider that since $\Gamma_r$ and $\Gamma_{r'}$ are full-dimensional, $\Gamma_{r'} \subseteq \Gamma_r \implies \Gamma_r \cap \Gamma_{r'} = \Gamma_{r'}$ is full dimensional, and we would observe $ r \in \Gamma(p)$ for all $p \in \inter{\Gamma_{r'}}$, contradicting unique optimality of the report $r'$ on the interior. 
We conclude $\Gamma'$ is nonredundant.

Consider $\strip(\Gamma') = \{\Gamma_r : r \in \R' \}$.
As $\R'$ is finite, so is $\strip(\Gamma')$.
Since $\Gamma'$ is a  nondegenerate, nonredundant property such that $\Gamma' \leq \Gamma$, we invoke the definition of trim to say $\trim(\Gamma) = \strip(\Gamma')$, so as $\strip(\Gamma')$ is finite, we conclude $\trim(\Gamma)$ is finite.

%We can rewrite $\strip(\Gamma) = \{\Gamma_{r'} : r' \in \R' \} \cup \{\Gamma_{r} : r \in \R \setminus \R' \}$.
%As the first set is finite, we just need to show $\{\Gamma_{r} : r \in \R \setminus \R' \}$ is finite in order to show $\strip(\Gamma)$ is finite.
%
%Let us consider some $r\in\R \setminus \R'$.
%The level set $\Gamma_r = \{p : \Gamma(p) = r\}$ by definition.
%As $r \not\in \R'$, the interior is empty; that is, $\inter{\Gamma_r} = \emptyset$.
%% For any $p \in \Gamma_r$, then, there is some $q \in B(\epsilon, p)$ such that $\E_q L(r', Y) < \E_q L(r,y)$ for some $r' \in \R'$.
%% As $r = \argmin_{\tilde{r}} \E_p L(\tilde{r}, Y)$, then we observe $\E_p L(r, Y) = \E_p L(r', Y) = \min_{\tilde{r}}\E_p L(\tilde{r}, Y)$ for $p \in \Gamma_r$. 
%% Thus, $\Gamma_r \subseteq \Gamma_{r'}$.
%By Conjecture \ref{lem:intersect-lev-sets}, there exist a set of finite reports $R \subseteq \R'$ such that $\bigcap_{r'\in R} \Gamma_{r'} = \Gamma_r$.
%As the set $\R'$ is finite, then the power set $2^{\R'}$ is finite.
%Thus, the set $\{ \Gamma_r : r \in \R \setminus \R' \} =  \{ \bigcap_{r_1 \in R} \Gamma_{r_1} : R \subseteq \R' \}$ is finite.
%
%
%The union of a two finite sets is then finite, so $\trim(\Gamma) \subseteq \strip(\Gamma) = \{ \Gamma_{r'} : r' \in \R' \} \cup \{ \Gamma_r : r \in \R \setminus \R' \}$ is finite.

\item[$2 \implies 1$]  
\emph{Assumptions used: Nondegeneracy, elicitability of $\Gamma$}

Let $\Theta := \trim(\Gamma)$ be a finite set.
By Conjecture~\ref{conj:gam-prime-exists}, there is then a nonredundant, nondegenerate property $\Gamma'$ such that $\strip(\Gamma') = \trim(\Gamma)$.
Let $\R' \subseteq \R$ be the finite set used to define the property $\Gamma'$.

As $\Theta$ is finite and $\trim(\Gamma)$ is the set of full dimensional level sets of $\Gamma$, the finite number of full-dimensional level sets follows from the assumption and definitions combined.

Consider a level set $\theta\in \Theta$.
There is a report $r \in \R'$ so that $\Gamma'(p) = \{r\}$ for all $p \in \inter{\theta}$-- this follows from nonredundancy of $\Gamma'$.

Therefore if the function $\trim(\Gamma)$ is well-defined and finite, then the labeled property $\Gamma$ has a finite set of full-dimensional level sets and for every $\theta \in \Theta$, there is a unique optimal report for every distribution $p \in \inter{\theta}$.

%Let $\Theta := \trim(\Gamma)$ be a finite set.
%By construction, $\Theta$ is a set of full dimensional level sets defining the property $\Gamma$.
%Thus, $\Gamma$ then only has finitely many \emph{full-dimensional} level sets.
%Then there is a finite set $\R' \subseteq \R$ defined by the property $\Gamma' \leq \Gamma$ where $\strip(\Gamma') = \trim(\Gamma)$.\jessie{Make sure I can claim this.}
%
%Consider a level set $\theta \in \Theta$.
%We want to show there is a unique $r \in \R'$ such that $\Gamma(p) = \{r\}$ for all $p \in \inter{\theta}$.
%
%Take the finite set $\R' \subseteq \R$ such that the nondegenerate, nonredundant property $\Gamma' \leq \Gamma$.
%Fix some level set $\theta \in \Theta$.
%For any $p \in \inter{\theta}$, there is then a report $r \in \R'$ such that  $r \in \Gamma(p)$ by nondegeneracy of $\Gamma'$.
%We then want to show $r$ is unique.
%
%For contradiction, consider some $r' \in \R'$ such that $r \neq r'$.
%As $\trim(\Gamma) = \strip(\Gamma')$ contains only full dimensional level sets, then $\Gamma_r$ and $\Gamma_{r'}$ are both full dimensional, as is their intersection $\Gamma_r \cap \Gamma_{r'}$.
%Since we define $\Gamma'$ in a manner so that for all $r \in \R' \implies \Gamma_r = \Gamma'_r$, we then say $\Gamma_r \cap \Gamma_{r'} = \Gamma'_r \cap \Gamma'_{r'}$, which contradicts the nonredundancy of $\Gamma'$.
%Therefore we observe a contradiction, and conclude $r = r'$.
%Therefore, if $\trim(\Gamma)$ is finite, then the property $\Gamma$ has a finite set (namely, $\trim(\Gamma)$) of full dimensional level sets so that for every $\theta \in \Theta$, there is a unique optimal report $r$ for every $p \in \inter{\theta}$.

\end{enumerate}

@@

\section{To Do after meeting 9.24.18}

look at Rockefellar- algebraic interior
Appendix of complexity paper- the Bayes Risk must be strictly concave.

Order of To-Dos -- ordered by dependency
\begin{enumerate}
\item Show there exists a nondeg, nonred $\Gamma' \leq \Gamma$ that $\trim(\Gamma) = \strip(\Gamma')$. (Conjecture~\ref{conj:gam-prime-exists}) -- Done
\item Show every level set of the trim is Full Dimensional (Conjecture~\ref{conj:trim-full-dim}).
\item Proof of $2 \implies 1$-- Done-ish.
\end{enumerate}
